---
title: "Penguin Analysis"
author: "Vera D"
date: "`r Sys.Date()`"
output: bookdown::html_document2
bibliography: citations.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(palmerpenguins)
library(knitr) #has kable to look prettier
library(here)
#will find root starting thing
print(getwd())

source(here("R/predict.R"))


kable(head(penguins))
```

```{r,message=FALSE} 
library(tidyverse) ##message thing in references that hides the library
```

# Methods

```{r, message=FALSE, warning=FALSE, fig.alt="This is for a screen reader and this is a figure of the bill_length_mm on the x axis, and the fillter_lenth_mm on the y, colore by species of penguins", fig.cap="Pengins by fiipper length vs bill length."}
ggplot(penguins, aes(x = bill_length_mm,
                     y = flipper_length_mm,
                     color = species)) +
  geom_point()
```

```{r penguins-with-lines, echo=TRUE}
#| message=FALSE,
#| warning=FALSE,
#| fig.alt="This is for a screen reader and this is a figure of the bill_length_mm on the x axis, and the fillter_lenth_mm on the y, colore by species of penguins",
#| fig.cap="Pengins by fiipper length vs bill length. Vertical and Horizontal lines represent cutoffs from the function."
ggplot(penguins, aes(x = bill_length_mm,
                     y = flipper_length_mm,
                     color = species)) +
  geom_point() +
  geom_hline(yintercept = 205) +
  geom_vline(xintercept = 45)
```


#rendering knit will return error if test has error 

```{r}
penguins <- penguins %>% 
  drop_na() %>% #TODO drop NA values
  mutate(my_predict = map2_chr(bill_length_mm, flipper_length_mm, classify_penguin))
```

```{r}
penguins %>% count(species, my_predict)
```

#Results

our data has `r nrow(penguins)` rows.
Figure \@ref(fig:penguins-with-lines) has shows where function will cut off for classification.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


This is the penguins dataset, but here is citations for @7009056.
#References



